---
title: "Portfolio"
toc: false
---

```{r}
#| echo: false
library(htmltools)
```

::: {.portafolio-header}
<span class="portafolio-titulo-chip">Project Portfolio</span>

# End-to-end data projects

<p class="portafolio-descripcion">Personal projects that solve real problems: from the initial question to the working tool — scraping, processing, analysis and visualization included.</p>
:::

```{r}
#| echo: false
div(class = "proyecto-destacado",
  div(class = "proyecto-destacado-img",
    tags$a(href = "https://langab.github.io/visor_arriendos/viewer/", target = "_blank",
      tags$img(src = "../blog/posts/visor-arriendos/img/vista_mapa.jpg",
               alt = "Rental viewer map with properties across Santiago")
    )
  ),
  div(class = "proyecto-destacado-body",
    div(class = "tarjeta-etiqueta", "Personal project · Python · In production"),
    tags$h3(HTML("<img src='../img/icons/housing.svg' class='icono-inline' alt=''> Rental Viewer · Santiago")),
    tags$p(
      "A complete data pipeline to find an apartment in Santiago: multi-portal ",
      "scrapers, deduplication, geocoding with OpenStreetMap, price analysis by ",
      "comparable groups, and an interactive viewer with map (Leaflet), metrics ",
      "and temporal analysis. It updates itself daily and is published on ",
      "GitHub Pages."
    ),
    div(class = "skill-tags",
      span(class = "skill-tag", "Python"),
      span(class = "skill-tag", "Web scraping"),
      span(class = "skill-tag", "Playwright"),
      span(class = "skill-tag", "Leaflet · OSM"),
      span(class = "skill-tag", "GitHub Pages"),
      span(class = "skill-tag", "Automation")
    ),
    div(class = "proyecto-destacado-botones",
      tags$a(href = "https://langab.github.io/visor_arriendos/viewer/",
             target = "_blank", class = "btn-primario", "See it live →"),
      tags$a(href = "../blog/posts/visor-arriendos/index.html",
             class = "btn-secundario", "Read how I built it (Spanish)"),
      tags$a(href = "https://github.com/Langab/visor_arriendos",
             target = "_blank", class = "btn-secundario", "Code on GitHub")
    )
  )
)
```

## <img src="../img/icons/toolbox.svg" class="icono-titulo" alt=""/> R scripts & analyses {.seccion-titulo}

::: {.callout-note appearance="simple"}
**In preparation** — I'm curating a collection of **R scripts** on data processing, statistical analysis and visualization developed in research and institutional projects. In the meantime, check my [publications](../publicaciones-en.qmd) and [work](../trabajos-en.qmd).
:::
