---
title: "Portfolio"
toc: true
toc-title: "Contents"
---

```{r}
#| echo: false
library(htmltools)
library(purrr)
```

<!-- ====================================================
     📁 PORTFOLIO HEADER
======================================================= -->

```{r}
#| echo: false

div(class = "portafolio-header",
  tags$span(class = "portafolio-titulo-chip", "📊 Scripts Portfolio"),
  tags$h1("R Scripts · Data Processing, Analysis & Visualization"),
  tags$p(class = "portafolio-descripcion",
         "A collection of practical R scripts on data processing, statistical analysis, and information visualization that I have developed in research and institutional projects.")
)
```

---

## 🚀 Coming Soon {.seccion-titulo}

::: {.callout-info appearance="simple"}
📌 **Status:** Under construction

I'm preparing a collection of **R scripts** featuring:
- **Data Processing:** cleaning, transformation, and normalization with `tidyverse`
- **Statistical Analysis:** exploratory analysis, statistical models, and hypothesis testing
- **Visualization:** plots with `ggplot2`, interactive dashboards, and dynamic reports

Each script will include:
- 📝 Detailed code explanation
- 🎯 Use cases and practical applications
- 💾 Available downloads
- 🔗 GitHub repository

Come back soon to explore the scripts! 🎉
:::

---

## 📂 Categories {.seccion-titulo}

```{r}
#| echo: false

categorias <- list(
  list(
    titulo = "🔄 Data Processing",
    icon = "📥",
    desc = "Scripts for data cleaning, transformation, and normalization with tidyverse. Handling missing values, deduplication, and database restructuring.",
    count = "Coming Soon"
  ),
  list(
    titulo = "📊 Statistical Analysis",
    icon = "📈",
    desc = "Exploratory data analysis (EDA), analysis of variance, regressions, linear models, and statistical inference tools."
  ),
  list(
    titulo = "🎨 Visualization & Infographics",
    icon = "🎯",
    desc = "Advanced plots with ggplot2, thematic maps, interactive dashboards with Shiny, and dynamic reports with Quarto.",
    count = "Coming Soon"
  ),
  list(
    titulo = "🤖 Special Techniques",
    icon = "⚙️",
    desc = "Text mining, network analysis, time series analysis, predictive modeling, and applied machine learning.",
    count = "Coming Soon"
  )
)

div(class = "grid portafolio-grid",
  map(categorias, \(cat) {
    div(class = "g-col-12 g-col-md-6",
      div(class = "portafolio-card-categoria",
        div(class = "portafolio-card-header",
          tags$span(class = "portafolio-icon", cat$icon),
          tags$h3(class = "portafolio-card-titulo", cat$titulo)
        ),
        tags$p(class = "portafolio-card-desc", cat$desc),
        tags$div(class = "portafolio-card-badge", cat$count)
      )
    )
  })
)
```

---

## 📚 Latest Scripts Added {.seccion-titulo}

```{r}
#| echo: false

div(class = "portafolio-empty",
  tags$span(class = "portafolio-empty-icon", "⏳"),
  tags$h4("Scripts will be available very soon"),
  tags$p("We are preparing a carefully curated selection of scripts ready to share.")
)
```

---

## 💬 Do you have a question? {.seccion-titulo}

::: {.callout-note appearance="simple"}
If you have questions about methodology, data processing, or statistical analysis with R, you can:

📧 **Email me:** [benjalang1997@gmail.com](mailto:benjalang1997@gmail.com)
🔗 **LinkedIn:** [View profile](https://www.linkedin.com/in/benjamin-lang-a78229207/)

I'd love to help you with your analysis! 🙌
:::
